Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-07-14 src/tex/ms.tex
address Ref#1 Com#1

\textit{Prevalent water inventory}: The magnitude of radius change at the runaway greenhouse threshold is sensitive to the water mass fraction.
As a result, the statistical abundance of water in terrestrial planets impacts the strength of the demographic pattern:
The higher the water content and the higher the fraction of planets in runaway greenhouse climates, the greater the likelihood that a discontinuity is detectable.
However, dissolution into the magma ocean and atmospheric inflation show non-linear coupling; thus, a straightforward trend is difficult to discern.

>>>>

\textit{Prevalent water inventory}: The magnitude of radius change at the runaway greenhouse threshold is sensitive to the water mass fraction.
As a result, the statistical abundance of water in terrestrial planets impacts the strength of the demographic pattern:
The higher the water content and the higher the fraction of planets in runaway greenhouse climates, the greater the likelihood that a discontinuity is detectable.
However, dissolution into the magma ocean and atmospheric inflation show non-linear coupling\rev{:
the more water there is in the atmosphere, the more will be dissolved~\citep{Dorn2021}, leading to a convergence in radii until saturation.
Most important for the present work, however, is the qualitative dichotomy between sub-runaway and runaway planets, which outcompetes radius variations within each of these climate states due to a changing water mass fraction~\citep{Turbet2020}.
If a planet hosts a significant water inventory that is not easily stripped by atmospheric escape~\citep{Johnstone2020}, then the statistical power of our model is high (see Figure~\ref{fig:statpwr_H2O-f}).
}
